WHOOMP! (There It Is) \\ Rapid Bayesian position reconstruction for gravitational\nobreakdashes-wave transients

### 2014-05-22 ms.tex
Reword description of MCMC

Bayesian parameter estimation has many advantages, including broad generality and the ability to make probabilistically meaningful statements even with very low \ac{SNR} measurements. However, in problems of even modest complexity, the marginalization step burdens the analysis with nasty, many-dimensional, ill-behaved integrals. Almost all modern parameter estimation tactics are variations of \ac{MCMC} integration. Though powerful, \ac{MCMC} is historically slow and non-deterministic. With the most sophisticated \ac{CBC} parameter estimation codes, it still takes days to process a single event. This delay is undesirable for planning targeted \ac{EM} follow\nobreakdashes-up searches of \ac{LIGO} events.

>>>>

Bayesian parameter estimation has many advantages, including broad generality and the ability to make probabilistically meaningful statements even with very low \ac{SNR} measurements. However, in problems of even modest complexity, the marginalization step involves many-dimensional, ill-behaved integrals. The powerful \ac{MCMC} integration technique has become almost synonymous with Bayesian inference. Though powerful, \ac{MCMC} is inherently non-deterministic and resistant to parallelization, as well as (at least historically) slow. With the most sophisticated \ac{CBC} parameter estimation codes, it still takes days to process a single event. This delay is undesirable for planning targeted \ac{EM} follow\nobreakdashes-up searches of \ac{LIGO} events.
